Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
Grammar and wording

\noindent First, we introduce new Haddock markup for the example.
In this paper, we use {\tt >>>} which is the same as Python's one.
Here is an example:

@@

\noindent Of course, we allowed quantified properties by using closed
lambda terms. The property example in Section~\ref{sec:doctest-haddock}
can be written as follows:

@@

Evidence in comments are automatically
tested by the Doctest command. We also provided a library
to do this job. Its implementation will discussed in Section~\ref{sec:doctest}.

@@

We propose following extensions for Hspec to
describe evidence for developers.

>>>>

\noindent First, we introduce new Haddock markup for examples.
In this paper, we use {\tt >>>} which is the same as Python's one.
Here is an example:

@@

\noindent Of course, we allow quantified properties by using a
lambda expression. The property example in Section~\ref{sec:doctest-haddock}
can be written as follows:

@@

Evidence in comments is automatically
tested by the Doctest command. We also provided a library
to do this job. Its implementation will discussed in Section~\ref{sec:doctest}.

@@

We propose the following extensions for Hspec to
describe evidence for developers.
